Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-09-25 doc/part-hydras.tex
Wainer-Hardy -> Hardy

Definition CompSpec {A} (eq lt : A->A->Prop)(x y:A) : comparison -> Prop :=
 CompareSpec (eq x y) (lt x y) (lt y x).
\end{Coqsrc}

@@

\section{A variant of the Wainer-Hardy hierarchy}

@@

In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the  \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

@@

\begin{remark}
 The ``classic'' definition of the Wainer-Hardy hierarchy differs in the third equation.

>>>>

Definition CompSpec {A} (eq lt : A -> A -> Prop) (x y : A) :=
 CompareSpec (eq x y) (lt x y) (lt y x).
\end{Coqsrc}

@@

\section{A variant of the Hardy hierarchy}

@@

In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the  \emph{Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

@@

\begin{remark}
 The ``classic'' definition of the Hardy hierarchy differs in the third equation.
